\bfseries\large Phosphatidylinositol 4,5-bisphosphate regulates cilium transition zone maturation in \textit{Drosophila melanogaster}

### 2018-02-20 latex/paper.tex
updated

\section{Discussion}
Cilia are essential for proper human development, and their disruption
can cause genetic disorders with severities ranging from congenital-
lethal \citep{}
to late onset \citep{}.
A large number of ciliopathies are associated with genes that encode for
proteins that function at the cilium transition zone (TZ).
Often, a single gene is linked to multiple ciliopathies with distinct phenotypes
and severities.
For example, \textit{CEP290} is linked to at least six different
cilium-associated disorders.
It is likely that these mutations do not completely abolish CEP290
function, and may be affected by genetic modifiers in an affected individual
\citep{zaghloul2010functional}.
Animal models with partial loss of TZ function may therefore provide
insight on intermediate phenotypes associated with human disease.
Here, we found that reduced levels of the membrane lipid \PIP{},
which is known to be enriched at the base of cilia,
affects TZ maturation, but not assembly,
leading to hyperelongated TZs that show signs of functional defects, and
may represent one such modifier for TZ function.

@@

The type I phosphatidylinositol 4-phosphate kinase (PIPKI) Skittles
suppresses TZ elongation in \sigd{} cells in a cilium-autonomous
manner.
We also found that cells mutant for \textit{sktl} contained hyperelongated
TZs similar to SigD-expressing cells.
Sktl also localizes to centrioles,
and our results suggest that Skittles acts locally at cilia to
regulate TZ length.
PIPKI$\gamma$ is linked to lethal congenital contractural syndrome
type 3 (LCCS3).
It has previously been suggested that LCCS3 might represent a ciliopathy.
PIPKI$\gamma$ is linked to LCCS3 with features reminiscent
of ciliopathies such as micrognathia, and a role for the LCCS1 protein
Gle3 in cilia.
In addition, all three human PIPKI isoforms are highly expressed in testes
and PIPKI$\alpha$ and PIPKI$\beta$ are important for fertility in mice
\citep{hasegawa2012phosphatidylinositol}.

@@

%\begin{figure}[ht]
%  \includegraphics[scale=0.9]{figure-3/figure2.png}
%\end{figure}
\newpage

@@

%\begin{figure}[ht]
%  \includegraphics[scale=0.9]{figure-4/figure2.png}
%\end{figure}
%\newpage

>>>>

\section{Discussion}
Cilia are essential for proper human development, and their disruption
can cause genetic disorders with severities ranging from congenital-
lethal \citep{}
to late onset \citep{}.
A large number of ciliopathies are associated with genes that encode for
proteins that function at the cilium transition zone (TZ).
Often, a single gene is linked to multiple ciliopathies with distinct phenotypes
and severities.
For example, \textit{CEP290} is linked to at least six different
cilium-associated human disorders.
It is likely that these mutations do not completely abolish CEP290
function, and may be affected by genetic modifiers in an affected individual
\citep{zaghloul2010functional}.
Animal models with partial loss of TZ function may therefore provide
insight on intermediate phenotypes associated with human disease.
Here, we found that reduced levels of the membrane lipid \PIP{},
which is known to be enriched at the base of cilia,
affects TZ maturation, but not assembly,
leading to hyperelongated TZs that show signs of functional defects, and
may represent one such modifier for TZ function.

@@

We found that the type I phosphatidylinositol 4-phosphate kinase (PIPKI) Skittles
suppresses TZ elongation in \sigd{} cells in a cilium-autonomous
manner.
We also found that cells mutant for \textit{sktl} contained hyperelongated
TZs similar to SigD-expressing cells.
Sktl also localizes to centrioles,
and our results suggest that Skittles acts locally at cilia to
regulate TZ length.
PIPKI$\gamma$ is linked to lethal congenital contractural syndrome
type 3 (LCCS3).
It has previously been suggested that LCCS3 might represent a ciliopathy.
PIPKI$\gamma$ is linked to LCCS3 with features reminiscent
of ciliopathies such as micrognathia, and a role for the LCCS1 protein
Gle3 in cilia.
In addition, all three human PIPKI isoforms are highly expressed in testes
and PIPKI$\alpha$ and PIPKI$\beta$ are important for fertility in mice
\citep{hasegawa2012phosphatidylinositol}.

@@

\begin{figure}[ht]
  \includegraphics[scale=0.8]{figure-3/figure3.png}
\end{figure}
\newpage

@@

\begin{figure}[ht]
  \includegraphics[scale=0.9]{figure-4/figure4.png}
\end{figure}
\newpage
